The \dealii Library, Version 9.5

### 2023-05-04 9.5/paper.tex
Stub for a language modernization section.
Some updates.

The major changes of this release are:
%
\begin{itemize}
  \item Integration of \texttt{Kokkos} (see Section~\ref{sec:kokkos});
  \item Update of the \texttt{PETSc} infrastructure (see Section~\ref{sec:petsc});
  \item Addition of new \texttt{Trilinos} wrappers (see Section~\ref{sec:trilinos});
  \item Advances in matrix-free infrastructure (see Section~\ref{sec:mf});
  \item Advance in non-matching support (see Section~\ref{sec:nonmatching});
  \item New liner algebra features (see Section~\ref{sec:lac}).
\end{itemize}
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Update of the PETSc infrastructure}\label{sec:petsc}

\begin{itemize}
\item PreconditionBDDC
\end{itemize}

@@

>>>>

The major changes of this release are:
%
\begin{itemize}
  \item Integration of \texttt{Kokkos} (see Section~\ref{sec:kokkos});
  \item Update to and extension of the \texttt{PETSc} wrappers (see Section~\ref{sec:petsc});
  \item Addition of new \texttt{Trilinos} wrappers (see Section~\ref{sec:trilinos});
  \item Advances in matrix-free infrastructure (see Section~\ref{sec:mf});
  \item Advance in non-matching support (see Section~\ref{sec:nonmatching});
  \item New liner algebra features (see Section~\ref{sec:lac})l
  \item C++ language modernization (see Section~\ref{sec:language}).
\end{itemize}
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Update of and additions to the PETSc wrappers}\label{sec:petsc}

\begin{itemize}
\item PreconditionBDDC
\item SNES
\item TS
\item Wrapping PETSc matrices and vectors
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{C++ language modernization}\label{sec:language}

Mention the C++20 work. Starting point: \dealii{} relies heavily on
templates that are explicitly instantiated.
